SUPPORTING INFORMATION:\\ Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-09-04 Manuscript/manuscriptPSsuppl.tex
Structure without additional ions

\clearpage
%\section{Details of the rough subjective force field ranking (Fig.~\ref{comparisonTablePS})}

\section{Details of the force field ranking (Fig.~\ref{comparisonTablePS})}\label{Ranking} 
In Figure~\ref{comparisonTablePS} of main text we present a rough and subjective ranking of the force fields investigated in this work. 
The assessment was based on the data presented in Fig.~\ref{HGorderParametersPS}.
%
For each carbon (the columns in Fig.~\ref{HGorderParametersPS}),
we first investigated separately how well a given force field represents the {\bf magnitude} of the order parameters and their {\bf forking}.

\subsubsection*{Magnitude}
To quantify how close to the experimentally obtained C--H order parameters ($S_\mathrm{CH}$s) were to the 
the force-field-produced $S_\mathrm{CH}$s, we assign a number for each carbon based on the following 5-step scale:

@@

\noindent Based on these assessments of magnitude and forking deviations from experimental values,
each carbon was then assigned to one of the following groups: "within experimental error"
(magnitude and forking deviations both on 0 of the scales described above),
"almost within experimental error"
(sum of the magnitude and forking deviation 1 or 2),
"clear deviation from experiments"
(sum of magnitude and forking deviation from 3 to 5), and
"major deviation from experiments"
(sum of magnitude and forking deviation from 6 to 8).
These groups are indicated by colors in Fig.~4.
(Note that for $\beta$ and $\mathrm{g_2}$, for which there can be no forking,
the corresponding group assignment limits were: 0, 1, 2, and 3.)

Finally, the total ability of the force field to describe the headgroup and
glycerol structure was estimated.
To this end, the groups were given the following weights:
0 (within experimental error),
1 (almost within experimental error),
2 (clear deviation from experiments),
4 (major deviation from experiments),
and the contributions from the five carbons were summed up.
The sum, given in the $\Sigma$-column of Fig.~\ref{HGorderParametersPS},
was then used to (roughly and subjectively) rank the force fields.

>>>>

\clearpage

\section{Details of the force field ranking (Fig.~\ref{comparisonTablePS})}\label{Ranking} 
In Fig.~\ref{comparisonTablePS} of main text we present a rough and subjective ranking of the force fields investigated in this work. 
The assessment was based on the data presented in Fig.~\ref{HGorderParametersPS}.
%
For each carbon (the columns in Fig.~\ref{HGorderParametersPS}),
we first investigated separately how well a given force field represents the {\bf magnitude} of the order parameters and their {\bf forking}.

\subsubsection*{Magnitude}
To quantify how close to the experimentally obtained C--H order parameters ($S_\mathrm{CH}$:s)
the force-field-produced $S_\mathrm{CH}$:s were, we assigned a number for each carbon based on the following 5-step scale:

@@

\noindent Based on these assessments of magnitude and forking deviations from experimental values,
each carbon was then assigned to one of the following groups: "within experimental error"
(magnitude and forking deviations both on 0 of the scales described above),
"almost within experimental error"
(sum of the magnitude and forking deviation 1 or 2),
"clear deviation from experiments"
(sum of magnitude and forking deviation from 3 to 5), and
"major deviation from experiments"
(sum of magnitude and forking deviation from 6 to 8).
These groups are indicated by colors in Fig.~\ref{comparisonTablePS}.
(Note that for $\beta$ and $\mathrm{g_2}$, for which there can be no forking,
the corresponding group assignment limits were: 0, 1, 2, and 3.)

Finally, the total ability of the force field to describe the headgroup and
glycerol structure was estimated.
To this end, the groups were given the following weights:
0 (within experimental error),
1 (almost within experimental error),
2 (clear deviation from experiments),
4 (major deviation from experiments),
and the contributions from the five carbons were summed up.
The sum, given in the $\Sigma$-column of Fig.~\ref{comparisonTablePS},
was then used to (roughly and subjectively) rank the force fields.
